\documentclass[12pt, letterpaper, preprint, comicneue]{aastex63}
%\usepackage[default]{comicneue} % comic sans font for editing
\usepackage[T1]{fontenc}
\input{vc}
\usepackage{color}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{ctable}
\usepackage{bm}
\usepackage[normalem]{ulem} % Added by MS for \sout -> not required for final version
\usepackage{xspace}
\usepackage{csvsimple} 

\usepackage{graphicx}
\usepackage{pgfkeys, pgfsys, pgfcalendar}


% typesetting shih
\linespread{1.08} % close to 10/13 spacing
\setlength{\parindent}{1.08\baselineskip} % Bringhurst
\setlength{\parskip}{0ex}
\let\oldbibliography\thebibliography % killin' me.
\renewcommand{\thebibliography}[1]{%
  \oldbibliography{#1}%
  \setlength{\itemsep}{0pt}%
  \setlength{\parsep}{0pt}%
  \setlength{\parskip}{0pt}%
  \setlength{\bibsep}{0ex}
  \raggedright
}
\setlength{\footnotesep}{0ex} % seriously?

% citation alias

% math shih
\newcommand{\setof}[1]{\left\{{#1}\right\}}
\newcommand{\given}{\,|\,}
\newcommand{\lss}{{\small{LSS}}\xspace}

\newcommand{\Om}{\Omega_{\rm m}} 
\newcommand{\Ob}{\Omega_{\rm b}} 
\newcommand{\OL}{\Omega_\Lambda}
\newcommand{\smnu}{M_\nu}
\newcommand{\sig}{\sigma_8} 
\newcommand{\mmin}{M_{\rm min}}
\newcommand{\BOk}{\widehat{B}_0} 
\newcommand{\hmpc}{\,h/\mathrm{Mpc}}
\newcommand{\bfi}[1]{\textbf{\textit{#1}}}
\newcommand{\parti}[1]{\frac{\partial #1}{\partial \theta_i}}
\newcommand{\partj}[1]{\frac{\partial #1}{\partial \theta_j}}
\newcommand{\mpc}{{\rm Mpc}}
\newcommand{\eg}{\emph{e.g.}}
\newcommand{\ie}{\emph{i.e.}}

% cmds for this paper 
\newcommand{\gr}{g{-}r}
\newcommand{\fnuv}{FUV{-}NUV}
\newcommand{\sfr}{{\rm SFR}}
\newcommand{\ssfr}{{\rm SSFR}}
\newcommand{\mtaum}{m_{\tau,M_*}}
\newcommand{\mtaus}{m_{\tau,{\rm SSFR}}}
\newcommand{\ctau}{c_\tau}
\newcommand{\mdeltam}{m_{\delta,M_*}}
\newcommand{\mdeltas}{m_{\delta,{\rm SFR}}}
\newcommand{\cdelta}{c_\delta}
\newcommand{\eda}{EDA}


\newcommand{\specialcell}[2][c]{%
  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}
% text shih
\newcommand{\foreign}[1]{\textsl{#1}}
\newcommand{\etal}{\foreign{et~al.}}
\newcommand{\opcit}{\foreign{Op.~cit.}}
\newcommand{\documentname}{\textsl{Article}}
\newcommand{\equationname}{equation}
\newcommand{\bitem}{\begin{itemize}}
\newcommand{\eitem}{\end{itemize}}
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}

%% collaborating
\newcommand{\todo}[1]{\marginpar{\color{red}TODO}{\color{red}#1}}
\definecolor{orange}{rgb}{1,0.5,0}
\newcommand{\ch}[1]{{\color{orange}{\bf CH:} #1}}

\begin{document} \sloppy\sloppypar\frenchspacing 

%\title{Measuring Unbiased Star Formation Histories: Correcting Model Imposed Priors}
\title{Mitigating Model Priors in Galaxy Spectral Energy Distribution Fitting} 
\date{\texttt{DRAFT~---~\githash~---~\gitdate~---~NOT READY FOR DISTRIBUTION}}

\newcounter{affilcounter}
\author{ChangHoon Hahn}
\altaffiliation{changhoon.hahn@princeton.edu}
\affil{Department of Astrophysical Sciences, Princeton University, Peyton Hall, Princeton NJ 08544, USA} 

\begin{abstract}
    Models for galaxy star formation histories (SFHs), both parametric and
    non-parametric, impose strong priors on derived physical properties of
    galaxies. These priors significantly bias galaxy stellar mass, star
    formation rate, and metalicities inferred from fitting galaxy spectral
    energy distributions (SED) and therefore impact all of the main summary
    statistics used to investigate galaxy populations (\eg~stellar mass function, star
    formation rate-density, star-forming sequence). In this work, we
    %demonstrate that the \cite{handley} method can correct for these biases by
    present a method that can correct for these biases and imposing uniform, or
    uninformative, priors, on the physical properties. The method imposes a
    maximum-entropy transformation on the probability distributions of the SED 
    model parameters to force the physical properties into any specified 
    distribution. We demonstrate, using simulated galaxy spectra constructed
    from the IllustrisTNG hydrodynamical simulation, that with this method we
    can accurately recover the input SFHs with SED modeling. Lastly, we use 
    the method to infer the SFHs of galaxies in a low-redshift, volume-complete
    sample from the Galaxy and Mass Assembly (GAMA) Survey. The cosmic star 
    formation rate-density we derive from the inferred SFHs are in good
    agreement with direct observations. 
\end{abstract}

\keywords{
keyword1 -- keyword2 -- keyword3
}

% --- intro ---  
\input{intro}
% --- methods ---  
\input{maxent}
% --- results ---  
\input{results}
% --- summary ---  
\input{summary}

\section*{Acknowledgements}
It's a pleasure to thank
    Mariska Kriek, 
    Marius Millea, 
    Katherine Suess, 
    Jeremy Tinker, 
    Rita Tojeiro

\appendix

\bibliographystyle{mnras}
\bibliography{maxent} 
\end{document}
